\documentclass[11pt]{article}
\usepackage[giveninits,maxnames=99, backend=bibtex, sorting=none]{biblatex}
\usepackage[NoDate]{currvita}
\usepackage{unicode,url,parskip}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage[compact]{titlesec}
\usepackage[margin=1.25in]{geometry}
\usepackage{times}

\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\makeatletter
\def\@fnsymbol#1{\ensuremath{\ifcase#1\or \dagger \or * \else\@ctrerr\fi}}
\makeatother


\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\bibliography{pubs.bib}
\tolerance=600

\AtEveryBibitem{%
  \ifentrytype{inproceedings}{%
    \clearfield{year}%
    \clearfield{pages}%
    \clearfield{booktitle}%
    \clearfield{note}%
  }{%
  }%
}
\AtEveryBibitem{%
  \ifentrytype{misc}{%
    \clearfield{year}%
  }{%
  }%
}
\AtEveryBibitem{%
  \ifentrytype{article}{%
    \clearfield{pages}%
    \clearfield{volume}%
    \clearfield{number}%
    \clearfield{month}%
  }{%
  }%
}
\DeclareFieldFormat{labelnumberwidth}{}
\setlength{\biblabelsep}{2.5em}

\DeclareFieldFormat
  [article,book,inbook,incollection,inproceedings,patent,thesis,unpublished]
  {title}{{\em #1}}

\setlength{\cvlabelwidth}{5em}
\setlength{\cvlabelskip}{%
0.2\baselineskip
}%


\begin{document}
% \bibliographystyle{plain}
\begin{cv}{\vspace{-5em}}
  \begin{center}
    \huge
    \textbf{Pratyush Mishra}
  \end{center}

  \href{mailto:pratyush@berkeley.edu}{\texttt{pratyush@berkeley.edu}}\hfill
  \href{http://www.pratyushmishra.com}{\texttt{pratyushmishra.com}}

  {\large \textbf{Education}}
  \begin{itemize}
    \item[] PhD, \textsc{Computer Science} (\small$08/2016$\,-\,Present)\\
    \emph{University of California, Berkeley}

  \item[] BSc, \textsc{Electrical Engineering \& Computer Science} (\small$08/2012$\,-\,$05/2016$)\\
    \emph{University of California, Berkeley}
  \end{itemize}
  %
  {\large\textbf{Papers}}
  {
    \small
    \noindent
    \nocite{BuenzCMS20,MishraLSZP20,BoweCGMMW20,ChiesaHMMVW20,MishraPCCP18,ChiesaGLMMM17,CarliniMVZSSWZ16,HoLMHSW16,PortnoffLEMLW15}
    \printbibliography[title = {\small Conference publications}, type=inproceedings]
    \nocite{ChiesaLMZ21,LehmkuhlMSP21,BuenzCLMS20,BuenzMMTV19}
    \printbibliography[title = {\small Preprints}, type=misc]
  }
  \footnotetext[1]{Contribution order.}


  {\clearpage\large\textbf{Teaching}}
  \begin{itemize}
    \item[] \emph{Co-Instructor, {CS294-163}: Decentralized Security (Fa~'19)}\\
      {\small
        Together with Prof.~Raluca Ada Popa, I designed and taught a new course on the theory and practice of \emph{systems for decentralized security}. I created hands-on tutorials for students to get experience with the latest tools in the space, and also designed and graded homework.
      }
    \item[] \emph{Teaching Assistant, {CS161}: Computer Security (Sp~'19, Sp~'16)}\\
      {\small
      I taught sections, designed homeworks, and graded exams for the undergraduate computer security class at UC Berkeley.}
  \end{itemize}

  %
  {\large\textbf{Talks}}
  \begin{itemize}
    \item[] \emph{Proof-Carrying Data from Accumulation Schemes:} JHU Security Seminar, Stanford Security Seminar, zkStudyClub.
    \item[] \emph{\textsc{Delphi}: {A} Cryptographic Inference Service for Neural Networks:} RISE Lab Retreat~'20, TPMPC Workshop, USENIX Security~'20, PPML~'20.
    \item[] \emph{$\textsc{Marlin}$: Preprocessing {zkSNARKs} with Universal and Updatable {SRS}:}. zkSummit~'19.
    \item[] \emph{$\textsc{Zexe}$: Enabling Decntralized Private Computation:}. Stanford Blockchain Conference~'19, Bay Area Crypto Day~'19, PENCIL Workshop~'19, Zcon1, CESC~'19, Simons Institute Blockchain in Society Workshop, S\&P~20.

    \item[] \emph{$\textsc{Oblix}$: An Efficient Oblivious Search Index}: Bay Area Crypto Day~'18, S\&P~18, RISE Lab Retreat~'18.
    \item[] \emph{Decentralized Anonymous Micropayments}: 
      EUROCRYPT~2017, NYU Crypto Seminar, Rambus Inc, Bay Area Crypto Day~'16.
  \end{itemize}

  %
  {\large \textbf{Service}}
  \begin{itemize}
    \small
    \item[] \emph{External reviewer}:
      S\&P~2020,
      OSDI~2018,
      NSDI~2018,
      TCC~2017,
      NDSS~2018,
      CCS~2016,
      TCC~2016-B.
      % TODO: Add student adcomm service.

    \item[] \emph{Graduate Admissions Committee, UC Berkeley}.
  \end{description}
\end{cv}
\end{document}
