\documentclass[11pt]{article}
\usepackage{bibunits}
\usepackage[NoDate, ManyBibs]{currvita}
\usepackage{unicode,url,parskip}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage[compact]{titlesec}
\usepackage[margin=1.25in]{geometry}
\usepackage[urw-garamond]{mathdesign}

\bibliography{pubs.bib}

\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\makeatletter
\def\@fnsymbol#1{\ensuremath{\ifcase#1\or \dagger \or * \else\@ctrerr\fi}}
\makeatother


\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\tolerance=600
\begin{document}

\setlength{\cvlabelwidth}{6.78em}
\setlength{\cvlabelskip}{%
0.2\baselineskip 
}%

\begin{cv}{\vspace{-5em}}
  \begin{center}
    \huge
    \textbf{Pratyush Mishra}
  \end{center}

  \href{mailto:pratyush@berkeley.edu}{pratyush@berkeley.edu}\hfill
  \href{http://www.pratyushmishra.com}{\texttt{pratyushmishra.com}} 

  \begin{cvlist}{Education}
  \item[\small$08/2016$\,-\,Present] PhD, \textsc{Computer Science}\\
    \emph{University of California, Berkeley}

  \item[\small$08/2012$\,-\,$05/2016$] BSc, \textsc{Electrical Engineering \& Computer Science}\\
    \emph{University of California, Berkeley}
  \end{cvlist}
  \vspace{-1em}
  %
  {\large\textbf{Publications}}

  \emph{Conference papers}\vspace{0.5em}

    \small
    \begin{bibunit}[alpha]
      \nocite{ChiesaGLMMM17, CarliniMVZSSWZ16, HoLMHSW16, PortnoffLEMLW15}
    \putbib[pubs]
    \end{bibunit}
  %
  \begin{cvlist}{Teaching}
  \item[\small$01/2016$\,-\,$05/2016$] Teaching Assistant, \textsc{CS161}: Computer Security\\
    {\small
    Taught sections, designed homeworks, and graded examinations for the computer security class at UC Berkeley taught by Prof.~David Wagner and Prof.~Raluca Ada Popa.}
  \end{cvlist}
  %
  \begin{cvlist}{Talks}
    \small
  \item[\small$05/2017$] \emph{``Oblivious Indices via Hardware Enclaves''}. RISE Lab Retreat.
  \item[\small$05/2017$] \emph{``Decentralized Anonymous Micropayments''}. EUROCRYPT~2017.
  \item[\small$04/2017$] \emph{``Decentralized Anonymous Micropayments''}. NYU Crypto Seminar.
  \item[\small$02/2017$] \emph{``Decentralized Anonymous Micropayments''}. Rambus Inc.
  \item[\small$09/2016$] \emph{``Decentralized Anonymous Micropayments''}. Bay Area Crypto Day.
  \end{cvlist}
  \footnotetext[1]{Alphabetical order.}
  \footnotetext[2]{Equal student author contribution.}
  %
  \begin{cvlist}{Service}
    \small
  \item[\emph{External reviewer}]
  \item[\small $2017$] \emph{15\textsuperscript{th} Theory of Cryptography Conference} (TCC~2017).
  \item[\small $2016$] \emph{23\textsuperscript{rd} ACM Conference on Computer and Communications Security} (CCS~2016).
  \item[\small $2016$] \emph{14\textsuperscript{th} Theory of Cryptography Conference} (TCC~2016-B).
  \end{cvlist}
\end{cv}
\end{document}
